---
output: pdf_document
documentclass: report
geometry: margin=.5in
fontsize: 11pt
font: Roboto
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```
*The Bureau of the Budget and Management Research, Results Teams*

## City Service: `r unique(pms$"Service Name"[pms$"Service ID"==i])`

**Agency Name**: `r unique(data$"Agency Name"[data$"Program ID"==i])` 
\newline
**Pillar**: `r unique(data$"Objective Name"[data$"Program ID"==i])`
\newline
**Last Year's Budget**: `r scales::dollar(sum(data$"FY22 Adopted"[data$"Program ID"==i]))`
\newline
**Current Level of Service Budget**: `r scales::dollar(sum(data$"FY23 CLS"[data$"Program ID"==i]))`
<!-- \newline -->
<!-- **Proposed Budget*: `r scales::dollar(sum(data$"FY23 Proposal"[data$"Program ID"==i]))` -->

### Performance Data
```{r pm_table, echo = FALSE, warning = FALSE}

df <- filter(pms, `Service ID` == i) %>%
  select(-`Service Name`, -`Met`, -`Service ID`)
knitr::kable(df)
```

### Performance Questions and Responses
```{r impact_statements, echo = FALSE, results = 'asis', warning = FALSE}

df <- filter(impacts, `Service ID` == i) %>%
  ungroup() %>%
  select(`Question #`, `Service Question`, `Agency Response`)

for (n in range(df$`Question #`)) {
  cat(paste(df$`Service Question`[df$`Question #` == n], "\n\n", df$`Agency Response`[df$`Question #` == n], "\n\n"))
}
```
